Differences from our PPoPP Conference Paper \cite{KBP16}

### 2018-12-14 latex/toms/algorithm.tex

\subsection{NLS Algorithms}
This subsection deals with the nonnegative least squares solves needed to update the factor at each inner iteration of the algorithm (\cref{line:locNLS} in \Cref{alg:Par-NNCP-short}). Our framework is capable of supporting any alternating-updating solver~\cite{KBP16}. The NLS solvers which fit this framework and are implemented in our software package are Multiplicative Update~\cite{LS99}, Hierarchical Alternating Least Squares~\cite{CP2009}, Block Principal Pivoting~\cite{KP2011}, Alternating Direction Method of Multipliers~\cite{HSL2016} and Nesterov-type algorithm~\cite{LKLHS2017}. We briefly describe the different solvers below.

\subsubsection{Multiplicative Update (MU)}
\subsubsection{Hierarchical Alternating Least Squares (HALS)}
\subsubsection{Block Principal Pivoting (BPP)}
\subsubsection{Alternating Direction Method of Multipliers (ADMM)}
\subsubsection{Nesterov-type algorithm}

>>>>

\subsection{NLS Algorithms}
This subsection deals with the nonnegative least squares (NLS) solves needed to update the factor at each inner iteration of the algorithm (\cref{line:locNLS} in \Cref{alg:Par-NNCP-short}). The general problem to be solved in each inner iteration is a constrained least squares problem of the form,

\begin{align}
\M{X} \leftarrow \underset{\M{X} \ge 0}{\argmin} \left\lVert \M{A}\M{X} -\M{B}\right\rVert^2_F
\label{eqn:nls}
\end{align}

In the case of updating the local factor matrix $\Mn{H}{n}_{\V{p}}$ we need to solve~\ref{eqn:nls} with $\M{X} = \Mn{H}{n}_{\V{p}}$, $\M{A} = \Mn{S}{n}$ and $\M{B} = \Mn{M}{n}_{\V{p}}$. Our framework is capable of supporting any alternating-updating NLS solver~\cite{KBP16}. The NLS solvers which fit this framework and are implemented in our software package are Multiplicative Update~\cite{LS99}, Hierarchical Alternating Least Squares~\cite{CP2009}, Block Principal Pivoting~\cite{KP2011}, Alternating Direction Method of Multipliers~\cite{HSL2016} and Nesterov-type algorithm~\cite{LKLHS2017}. We briefly describe the different solvers below. Note that the descriptions are for the general form of the NLS solver as shown in~\ref{eqn:nls}.

\subsubsection{Multiplicative Update (MU)}
The MU solve is an elementwise operation. The update rule for each element of $\M{X}$ is as follows,
\begin{align}
\M{X}(i,j) \leftarrow \M{X}(i,j)\frac{\M{B}(i,j)}{\left(\M{A}\M{X}\right)(i,j)}
\end{align}
While this rule does not solve~\ref{eqn:nls} to optimality it ensures a reduction in the objective value from the initial value of $\M{X}$.

\subsubsection{Hierarchical Alternating Least Squares (HALS)}
HALS updates are performed on individual rows of $\M{X}$. The update rule for row $i$ can be written in closed form as,
\begin{align}
\M{X}(i,:) \leftarrow \left[ \M{X}(i,:) + \frac{\M{B}(i,:) - \left(\M{A}(i,:)\M{X}\right)}{\M{A}(i,i)} \right]_+
\end{align}
The rows of $\M{X}$ are updated in order so that the latest values are used in every update step.

\subsubsection{Block Principal Pivoting (BPP)}
\subsubsection{Alternating Direction Method of Multipliers (ADMM)}
\subsubsection{Nesterov-type algorithm}
